Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-05 thesis/paper.tex
Updates to RQ1 results

%%What she said 
The interviewee expressed to us that the main driving force behind this change was to re-implement and add new functionality to the axhttp module. Redesigning the module to take advantage of the new design was an added bonus.

@@

%%Describe the change 
The burst mode feature of the API allowed users to buffer a series of images for closer analysis. This feature was deprecated during the transition between 1.4 and 2.0 and was not re-implemented.

%%Relate it to Categories
This change presented itself as a clear example of a reductive category of maintenance as it was simply removed and not replaced within the API. We also concluded that this change had no secondary category.

%%What she said
The interviewee did shed some light onto why this change occurred. We were informed that in order to continue using this feature in 2.0 and in newer versions of the camera hardware, it would have to be re-implemented from scratch. An impact assessment was undertaken to determine if the removal of the function would cost significant time and money. Ultimately it was deemed appropriate and the function was removed from the API.

%%Category based on her information
Given this information we can safely say that we correctly categorised this as reductive that there are indeed no other secondary categories to describe this change.

@@

%%Describe the change 
As with many APIs, Axis included a selection of example programs to assist developers with creating applications. This trend continued in 2.0, but there were some significant improvements. The number of example programs increased, as did the amount of comments accompanying the code which has lead to an overall more robust set of examples.

@@

%%What she said
From the interview it became clear that the improvement of the example code was an important change between the two versions. The interviewee described to us how the examples were used frequently by their customers, however, the old examples varied significantly, even between similar tasks. This ultimately meant that the old examples were not good enough and new ones needed to be created, preferably conforming to a standard. The new example code explicitly covered the new functionality, focusing on new features and showing how they can be combined to create applications.

@@

%%Describe the change 
As the API changed versions, so too did the documentation. While there were no substantial changes, we did notice that the documentation is no longer offered as a PDF via latex but is instead only offered via HTML.

@@

@@

%%Describe the change 
Version 1.4 of the API allowed direct access to the headers of each module available in the API. Version 2.0 changed this by including interfaces from which users can now access functionality. This design change has had an overall affect on the whole API as it has changed the structure of modules, but not their functionality.

%%Relate it to Categories
We therefore concluded that this change would be best categorised as  groomative. The secondary category of preventive was also chosen as this change could be seen as an attempt to reduce future maintenance.

%%What she said
The interview provided further insight into the reasoning behind this design change. Improvements to the coding standards, the desire for an event driven system and difficulty in using the existing APIs were all contributors to the decision to change the interfaces of the API. Furthermore, the redesign would hopefully avoid future maintenance while allowing the system to be easily extended.

%%Category based on her information
Taking this information into account, we concluded that our categorisation was incorrect. The primary change seemed to be preventive given the strong emphasis on avoiding future maintenance and improving ease of use. We further concluded that the secondary change should be groomative reflect the intent to make the API more maintainable overall.

@@

%%Describe the change 
A substantial change included in version 2.0 was the addition of specific error header files, containing enums of error codes. While we were not aware of what error handling was utilised prior to this version, we assumed it had changed given the inclusion of these new files.

>>>>

%%What she said 
The interviewee expressed that the main driving force behind this change was to re-implement and add new functionality to the axhttp module, while at the same time, allowing them to the module according to the new design.

@@

%%Describe the change 
The burst mode feature of the API allowed users to buffer a series of images for more exact analysis. This feature was deprecated during the transition between version 1.4 and 2.0 and was not re-implemented.

%%Relate it to Categories
This change presented itself as a clear example of a reductive category of maintenance, as it was simply removed and was not replaced. We also concluded that this change had no secondary category.

%%What she said
The interviewee did shed some light onto why this change occurred. In order to continue using this feature in version 2.0 and in newer versions of the camera hardware, it would have to be re-implemented. An impact assessment was undertaken to determine if the removal of the function would be costly. Ultimately it was deemed appropriate and the function was removed from the API.

%%Category based on her information
Given this information, we can conclude that we correctly categorised this as reductive and that there are indeed no other secondary categories to describe this change.

@@

%%Describe the change 
The case company included a selection of example programs to assist developers with creating applications. This trend continued in 2.0, but there were some significant improvements. The number of example programs increased, as did the amount of comments accompanying the code which has lead to an more robust set of examples.

@@

%%What she said
From the interview it became clear that the improvement of the example code was an important change between the two versions. The interviewee described how the examples were used frequently by their customers, however, the old examples varied significantly, even between similar tasks. This ultimately meant that the old examples were not satisfactory and new ones needed to be created, preferably conforming to a standard. The new example code explicitly covered the new functionality, focusing on new features and showing how they can be combined to create applications.

@@

%%Describe the change 
As the API code was updated in version 2.0, the API documentation was updated to correspond with the new code. While there were no substantial changes, we found that the documentation is no longer offered as a PDF but is instead only offered as HTML.

@@

%Re-write this, don't say no information etc

@@

%%Describe the change 
Version 1.4 of the API allowed direct access to the headers of each module available in the API. Version 2.0 changed this by including interfaces through which functionality is accessed. This design change has had an effect on the whole API, as it has changed the structure of modules, but not the functionality of them.

%%Relate it to Categories
We therefore concluded that this change would be best categorised as  groomative. The secondary category was categorised as preventive, as this change could be seen as an attempt to reduce future maintenance.

%%What she said
The interview provided further insight into the reasoning behind this design change. Improvements to the coding standards, the desire for an event driven system and difficulty in using the existing APIs were all contributors to the decision to change the interfaces of the API. Furthermore, the redesign would hopefully avoid future maintenance while allowing the system to be more extensible.

%%Category based on her information
Taking this information into account, we concluded that our categorisation was incorrect. The interview showed that the primary categorisation should have been preventive, given the strong emphasis on avoiding future maintenance and improving ease of use. We further concluded that the secondary change should have been groomative to reflect the intent to make the API more maintainable.

@@

%%Describe the change 
A substantial change included in version 2.0 was the addition of header files, containing enums of error codes. While we were not aware of what error handling was utilised prior to this version, we assumed it had changed, given the inclusion of these new files.
